Music Recommendation System Using the Million Song Dataset

### 2015-05-09 writeup/MSDgroupwriteup.tex
Changing sub setting to subsetting

There are several hyperparameters that can be tweaked in order to achieve a better MAP result using matrix factorization. The main ones that we explored were the variance, the rank $d$ of the factorization, and the number of iterations. As the project was being done using Python and the main computational package (\emph{scikit-learn}) did not have probabilistic matrix factorization functions, we decided to apply the algorithm that we wrote ourselves for a different class \citep{koren2009matrix}. It should be noted that while PMF algorithms can be parallelized to significantly improve running time and scaled to handle large amounts of data, being limited to a single machine to run these computations meant that sub setting the data was necessary in order to actually execute the algorithm successfully while limiting computational time to durations that were feasible for exploration.

>>>>

There are several hyperparameters that can be tweaked in order to achieve a better MAP result using matrix factorization. The main ones that we explored were the variance, the rank $d$ of the factorization, and the number of iterations. As the project was being done using Python and the main computational package (\emph{scikit-learn}) did not have probabilistic matrix factorization functions, we decided to apply the algorithm that we wrote ourselves for a different class \citep{koren2009matrix}. It should be noted that while PMF algorithms can be parallelized to significantly improve running time and scaled to handle large amounts of data, being limited to a single machine to run these computations meant that subsetting the data was necessary in order to actually execute the algorithm successfully while limiting computational time to durations that were feasible for exploration.
